\chapter[Demographic Survey]{Demographic Survey}

\section{Background}

This survey was administered to PHYS 24100 students in the first week of the summer 2015 session. If students completed the survey, they received ten bonus points (equal to the weight of one quiz). It was used to collect general demographic data in order to assess the quality of the CITA program and learn about general trends in the course.

\section{Student Demographics Survey}

Please be sure to make an entry for each question before clicking the submit button. Once you submit a choice for a question, your answer cannot be changed for that question. However, if you submit your choices for only some of the questions, you can come back to this survey prior to the deadline and fill out the remainder of the choices later.

What is your class at Purdue?

\begin{enumerate}
	\item Freshman
	\item Sophomore
	\item Junior
	\item Senior
	\item Graduate
	\item Not Listed
\end{enumerate}

Are you on-campus or off-campus this summer?

\begin{enumerate}
	\item On-Campus
	\item Off-Campus
\end{enumerate}

What is your college/school at Purdue?

\begin{enumerate}
	\item Agriculture
	\item Education
	\item Engineering
	\item Exploratory Studies
	\item Health and Human Sciences
	\item Liberal Arts
	\item Management
	\item Pharmacy
	\item Science
	\item Technology
	\item Veterinary Medicine
	\item Not Listed
\end{enumerate}

If you are in the College of Engineering or the College of Science, what is your primary major?

\begin{enumerate}
	\item BIOL
	\item CHM
	\item CS
	\item EAPS
	\item MA
	\item PHYS
	\item STAT
	\item SCI
	\item AAE
	\item ABE
	\item BME
	\item CE
	\item CEM
	\item CHE
	\item ECE
	\item EEE
	\item ENE
	\item ENGR
	\item EPE
	\item IDE
	\item IE
	\item ME
	\item MSE
	\item NUCL
	\item I Am Not in Science or Engineering
\end{enumerate}

Are you a domestic or foreign student? A domestic student is a US citizen, US national, or resident alien of the United States.

\begin{enumerate}
	\item Domestic
	\item Foreign
\end{enumerate}

What is your racial/ethnic classification?

\begin{enumerate}
	\item American Indian or Alaska Native
	\item Asian
	\item Black or African American
	\item Hispanic or Latino
	\item Indian Subcontinent
	\item Native Hawaiian or Other Pacific Islander
	\item White
	\item Multiracial or Biracial
	\item Not Listed
\end{enumerate}

What is your gender?

\begin{enumerate}
	\item Man
	\item Woman
	\item Transgender
	\item Not Listed
	\item I Prefer Not to Disclose
\end{enumerate}

Is PHYS 24100 required or an elective for you?

\begin{enumerate}
	\item Required by your major/department
	\item Required by your school/university
	\item Elective
\end{enumerate}

If you satisfied the pre-requisite of PHYS 17200 by taking it at Purdue, select the grade you received (options 1-5). If not, select how you satisfied this requirement (options 6-8).

\begin{enumerate}
	\item A
	\item B
	\item C
	\item D
	\item PASS
	\item Physics Test-out Exam
	\item AP Credits
	\item Transfer Credits
\end{enumerate}

If you took PHYS 24100 at Purdue previously, please select the most recent grade that you received.

\begin{enumerate}
	\item A
	\item B
	\item C
	\item D
	\item F
	\item PASS
	\item NOT PASS
	\item I have not taken PHYS 24100
\end{enumerate}

What is your expected grade in this course?

\begin{enumerate}
	\item A
	\item B
	\item C
	\item D
	\item F
	\item PASS
	\item NOT PASS
\end{enumerate}

Did you take an electricity and magnetism course in high school?

\begin{enumerate}
	\item Yes, at a level comparable to PHYS 24100
	\item Yes, at a lower level than PHYS 24100"
	\item No
\end{enumerate}

What is the highest level of Calculus course you have taken and passed? Calc I is the first semester calculus (similar to MA161/165 at Purdue and typically includes plane analytic geometry and introduction to one-variable differential and integral calculus). Calc II is the second semester calculus (similar to MA162/166 and typically includes vectors in two and three dimensions, more integration techniques, various orthogonal coordinate systems, surfaces, etc.). Calc III is the third semester calculus (similar to MA261 and typically multivariate calculus).

\begin{enumerate}
	\item Calc I
	\item Calc II
	\item Calc III or higher
	\item I have never taken calculus
\end{enumerate}

If you took Calc I at Purdue, what grade did you receive in it (options 1-5)? If not, how did you satisfy Calc I (options 6-8)? Calc I is a pre-requisite for Calc II, which is a co-requisite for PHYS241.

\begin{enumerate}
	\item A
	\item B
	\item C
	\item D
	\item PASS
	\item By MA Test-out Exam
	\item By AP credits
	\item By Transfer Credits
	\item I have not satisfied this pre-requisite
\end{enumerate}

Please make any additional comments below:

[A text box is supplied here for any additional comments]
