\chapter[Focus Group Discussion Guide]{Focus Group Discussion Guide}

\section{Opening Remarks}

Thank you all for coming today. My name is [MODERATOR] and this is [NOTE TAKER]. We are conducting a study of the effectiveness of the interactive tutorials that you used on the homework this past semester. It is all well and good to update a system based on the test scores, but obviously, that only tells part of the story. You have all been working with the system, so you are the experts. We want to hear your opinions.

We want to hear your honest thoughts and opinions because that is how we can improve the system. I have prepared a set of questions for the session, but feel free to add in any extra comments as we go along. There are no right or wrong answers in this session.

During our discussion [NOTE TAKER] will be taking notes. However, [NOTE TAKER] cannot write down every word we say. With your permission, we would like to record the discussion so that we don’t miss anything that is said. Of course, this discussion will stay confidential and your comments will not affect your course grade in any way. Is it alright with everyone if we record the discussion?

During our discussion please let everyone share their views. Make sure that only one person is speaking at a time so that the recording will be clear. Just join in when you have something to say. If you feel like you want to share more details with me, just let me know after the session. I will schedule a private one-on-one interview at your convenience so you can tell me more about your opinions.

Everything that you hear today should be confidential and not shared with people who are outside the group. It is perfectly fine to disagree with others! This discussion will last about one and a half hours. At the end of the session, we will give you a gift card as a thank you for taking the time to participate in this study.

Please make sure that you turn off all of your cell phones and mobile devices.

Are there any questions before we start?

\section{Discussion Questions}

\subsection{Introduction}
The allotted time for this section is 15 minutes.

\begin{enumerate}
	\item What is your area of study here at Purdue?
	\begin{itemize}
		\item Engineering
		\item Science
		\item Other Majors
	\end{itemize}
	\item What was your experience with physics homework in high school and/or PHYS 17200?
	\begin{itemize}
		\item Online Homework Systems
		\item Written Homework Assignments
		\item Systems Paired with a Textbook
	\end{itemize}
	\item What is your normal work process for the interactive homework assignments?
	\begin{itemize}
		\item Start Time
		\item End Time
		\item Individual Work
		\item Group Work
		\item What Tools are Used
		\item Learning Goals
	\end{itemize}
\end{enumerate}

\subsection{Assessment of Structure}
The allotted time for this section is 30 minutes.

\begin{enumerate}
	\item How did the look of the website affect your learning?
	\begin{itemize}
		\item Graphics
		\item Diagrams
		\item Pictures
		\item Boxes
		\item Colors
	\end{itemize}
	\item What did you think of the flow of the website?
	\begin{itemize}
		\item Help Buttons
		\item Branching
		\item Navigation
		\item Returning to Earlier Sections
	\end{itemize}
\end{enumerate}

\subsection{Assessment of Content}
The allotted time for this section is 30 minutes.

\begin{enumerate}
	\item Did the content help you on specific homework problems?
	\begin{itemize}
		\item Relevancy of Tutorial
		\item Expectations of Assignment
		\item Giving Away Answers
		\item Step-by-Step Instructions
	\end{itemize}
	\item Did the content help you on the quizzes and exams?
	\begin{itemize}
		\item Similarity of Tutorials to Quizzes and Exams
		\item Seeing Parallels Between Homework and Exams
		\item Being Able to Answer a Question in Multiple Ways
	\end{itemize}
\end{enumerate}

\subsection{Summary and Closing}
The allotted time for this section is 15 minutes.

\begin{enumerate}
	\item Overall, do you feel that the interactive examples were helpful?
	\begin{itemize}
		\item Specific Reasons One Way or Another
	\end{itemize}
	\item Do you have any final ideas about how we can improve the system?
	\begin{itemize}
		\item Learning Goals of Students
	\end{itemize}
\end{enumerate}