\chapter[Student Exit Survey]{Student Exit Survey}

\section{Background}

This survey was administered to PHYS 24100 students in the final week of the summer 2015 session. It is a completely voluntary survey - no points or reimbursement of any kind was given to students who completed it. It was used to collect feedback about student experiences with the CITA program.

Each survey question (except for the ``General Questions'') could be answered in one of five ways:

\begin{enumerate}
	\item Strongly Agree
	\item Agree
	\item Neutral
	\item Disagree
	\item Strongly Disagree
\end{enumerate}

The first of the ``General Questions'' could be answered using:

\begin{enumerate}
	\item Strongly Satisfied
	\item Satisfied
	\item Neutral
	\item Dissatisfied
	\item Strongly Dissatisfied
\end{enumerate}

The second of the ``General Questions'' was answered using a text box.

\section{Student Exit Survey}

We are constantly trying to improve the online homework system and would like your feedback. Please assess each statement using the drop down menu. Your choices are ``Strongly Agree'', ``Agree'', ``Neutral'', ``Disagree'', and ``Strongly Disagree''.

Please be sure to make an entry for each question before clicking the submit button. Once you submit a choice for a question, your answer cannot be changed for that question. However, if you submit your choices for only some of the questions, you can come back to this survey prior to the deadline and fill out the remainder of the choices later.

Interactive Walkthroughs (i.e. The Help Buttons)

\begin{enumerate}
	\item I used the interactive walkthroughs to help me with homework problems.
	\item The interactive walkthroughs helped me learn the material.
	\item The interactive walkthroughs increased my workload for the semester.
	\item The interactive walkthroughs increased communication between me and other students.
\end{enumerate}

Followup Questions (i.e. The Purple Box Following Each Question)

\begin{enumerate}
	\item I tried to answer the followup questions on each homework assignment.
	\item The followup questions helped me learn the material.
	\item The followup questions increased my workload for the semester.
	\item The followup questions increased communication between me and other students.
\end{enumerate}

General Questions

\begin{enumerate}
	\item What is your overall satisfaction with the interactive homework system?
	\item Do you have any general comments that you would like to share? Would you be willing to talk to us to provide more details (if so, write down your name and contact information)?
\end{enumerate}
